I am writing to express my interest in the Work Learn Software Programmer position in the UBC Civil Engineering Department.
I am currently pursuing a Bachelor of Applied Science in Computer Engineering at UBC, and have a solid foundation in
C++ programming.

At Douglas College, I took a formal object oriented programming course where we used C++ to do our assignments and labs.
We did daily labs, and I was able to learn the core ideas behind creating classes, data abstractions, organizing code into
different header files, constructors/deconstructors, and dynamic memory allocation/deletion. I have also implemented many
fundamental data structures, such as queues, stacks, binary heaps, binary search trees, etc using C++ in a data structures and
algorithms course.


Furthermore, I have taken CPSC 210 at UBC, a software construction course that emphasized software design, implementation,
and comprehensive unit testing. I learned to read existing codebases and write code that is both readable
and maintainable. Additionally, in CPSC 304, I worked within a team to design a relational database to store game
data for League of Legends. The project allowed users to make informed strategy decisions by querying analytics through a user friendly front-end
interface. In both courses, I gained hands-on experience with version control using Git, becoming comfortable working in my own
local branch, and submitting pull requests for team code reviews in a team setting.

My goal is to make meaningful contributions to the software and have it valued by any engineers
using it. I hope to exponentially improve my software development skills while being guided by a professional. In the past, I have coordinated with civil engineers
specializaing in structural analysis while performing concrete foundation repairs in residential and commercial settings. I understand that
their work carries serious consequences if not executed with precision. I will apply an equal amount of precision and professionalism when writing software
that could be used by other engineers for similar critical purposes.

I believe that my experience in C++ and my desire to work hard makes me a strong candidate for this position. Thank you for
considering my application.



